
% Thesis Abstract -----------------------------------------------------


%\begin{abstractslong}    %uncommenting this line, gives a different abstract heading
\begin{abstracts}        %this creates the heading for the abstract page

The main subject of this thesis addresses the possibility of enhancing the existing 3D reconstruction algorithms with additional Android sensor fusion data. The primary fundamentals behind the reconstruction techniques and the problems related to them are explained in order to introduce the reader to these topics. Related works are discussed in order to explain the strengths and weaknesses of the state-of-art reconstruction approches. The proposed enhancements using initial rotation in the standard 8-point and 5-point algorithms are explained in detail. Both of them allow for focusing on correcting rotation matrix error instead of calculating the rotation itself. This, in turn, serves for reducing ambiguity of the decomposition of essential matrix to the relative rotation and translation of the cameras. The primary idea behind the implementation of the 3-point algorithm for translation is also described. The most important aspects of the implemented $"Sensor Enhanced Image Camera"$ Android application and $"Enhanced 3D Reconstructer"$ were discussed.
The three proposed initial pair reconstruction methods were evaluated, which showed that each algorithm is able to improve certain asspects of the 3D reconstruction. Different reconstruction strategies were evaluated. As a result it was discovered that the enhanced structure computation can be faster and more accurate than the standard methodology. Using initial rotation and translation pose estimation results in significantly faster convergence and better error reduction with Bundle Adjustment. This thesis covers only some notions of the Structure from Motion, therefore plans for future development were  established.

\end{abstracts}
\clearpage
\renewcommand{\abstractname}{Zusammenfassung}
\begin{abstracts}        %this creates the heading for the abstract page

Das Hauptthema dieser Arbeit befasst sich mit der M{\"o}glichkeit der Verbesserung der vorhandenen 3D-Rekonstruktionsalgorithmen mit zus{\"a}tzlichen Android Sensorfusion Daten. Die wichtigsten Grundlagen hinter den Rekonstruktionstechniken und die damit verbundenen Probleme sind, um den Leser zu diesen Themen vorstellen erl{\"a}utert. {\"A}hnliche Arbeiten sind erforderlich, um die Festigkeiten und Schw{\"a}chen der Stand-der-Technik Rekonstruktion Ansätze erkl{\"a}ren diskutiert. Die vorgeschlagenen Verbesserungen mit Anfangsrotation in den Standard 8-Punkte und 5-Punkte-Algorithmen werden im Detail erkl{\"a}rt. Beide von ihnen k{\"o}nnen zur Fokussierung auf die Rotationsmatrix Fehler Korrektur anstelle der Berechnung des Rotation selbst. Dies wiederum serviert zur Reduzierung der Mehrdeutigkeit des Essential-Matrix Zersetzungs zu der relativen Rotation und Translation den Kameras. Die Hauptidee hinter der Umsetzung der 3-Punkt-Algorithmus f{\"u}r die Translation ist ebenfalls beschrieben. Die wichtigsten Aspekte die implementierten $"Sensor Verbesserte Bildkamera "$ Android-Anwendung und $ "Verbesserte 3D Reconstructer "$  wurden diskutiert.
Die drei vorgeschlagenen ersten Paar Rekonstruktionsmethoden wurden bewertet, die zeigten, dass jeder Algorithmus kann bestimmte asspects der 3D-Rekonstruktion zu verbessern. Verschiedene Rekonstruktionsstrategien wurden bewertet. Als Ergebnis wurde festgestellt, dass die verbesserte Struktur Berechnung kann schneller und genauer als die Standardmethode sein. Mit  anfänglichen Rotation und Translation  Posenschätzung resultiert in signifikant schneller Konvergenz und besseres Fehlerreduktion mit B{\"u}ndelausgleichung. Diese Diplomarbeit umfasst nur einige Vorstellungen von der Struktur aus Bewegung, daher plant f{\"u}r die zuk{\"u}nftige Entwicklung entstanden.

\end{abstracts}
%\end{abstractlongs}


% ---------------------------------------------------------------------- 
